---
title: "FinalProject"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
In our project, we are comparing the relative stats and draft order of players in a certain position and how it relates to the money they make in their first contract. For each position we have at least 2 statistics (draft order and skill statistic) that we will compare against first contract earned to see if there is any relation between draft order or performance that relates to earning a contract. In total, we have 6 position groups to analyze, and we have pulled data from draft years 2010 to 2013.
```{r}
setwd("~/Spring/Stat/Final")
QB_Data <- read.csv("QB_Data.csv")
RB_Data <- read.csv("RB_Data.csv")
WR_Data <- read.csv("WR_Data.csv")
DL_Data <- read.csv("DL_Data.csv")
LB_Data <- read.csv("LB_Data.csv")
DB_Data <- read.csv("DB_Data.csv")
```
```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
```

The first position group we will be analyzing are the Quarterbacks.
```{r}
DraftOrders <- QB_Data$Draft.Order
AvgDraftOrder <- mean(DraftOrders)
```
The average draft order of the Quarterbacks we selected was:
```{r}
AvgDraftOrder
```
The median draft order was:
```{r}
MedianDraftOrder <- median(DraftOrders)
MedianDraftOrder
```
The mode of the draft order was:
```{r}
ModeDraftOrder <- Mode(DraftOrders)
ModeDraftOrder
```
The measures of central tendency for draft order is listed below (Range, Variation, and Standard Deviation)
```{r}
RangeDraftOrder <- 
```


For Quarterbacks we have selected one statistic that combines all individual data points of quarterbacks (completion percentage, touchdowns, yard thrown, etc.)
```{r}
QBR <- QB_Data$QBR
AvgQBR
```