---
title: "FinalProject"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
In our project, we are comparing the relative stats and draft order of players in a certain positional side (Offense vs Defense) and how it relates to the money they make in their first contract. For each side of the ball we have at 2 statistics (draft order and average salary) that we will compare against first contract earned to see if there is any relation between draft order or performance that relates to earning a contract. In total, we have 6 positional groups (3 on each side of the ball) to analyze, and we have pulled data from draft years 2010 to 2013. In our final write-up we will go more in depth by position and analyze their skill statistics versus their average salaries after their rookie year.
```{r}
#setwd("~/Spring/Stat/Final")
setwd("~/Desktop/BokeyZhangFinalR")
QB_Data <- read.csv("QB_Data.csv")
RB_Data <- read.csv("RB_Data.csv")
WR_Data <- read.csv("WR_Data.csv")
DL_Data <- read.csv("DL_Data.csv")
LB_Data <- read.csv("LB_Data.csv")
DB_Data <- read.csv("DB_Data.csv")
Offense <- read.csv("Offense.csv")
Defense <- read.csv("Defense.csv")
```
```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

FindOutliers <- function(x) {
  lowerq = quantile(x)[2]
  upperq = quantile(x)[4]
  iqr = upperq - lowerq
  extreme.threshold.upper = (iqr * 3) + upperq
  extreme.threshold.lower = lowerq - (iqr * 3)
  result <- which(x > extreme.threshold.upper | x < extreme.threshold.lower)
}
```

The first positional side we are discussing will be the Offensive side (3 positions - QB, RB, and WR)
```{r}
OffenseDraftOrders <- Offense$Draft.Order
OffenseSalary <- Offense$Avg.Salary..million.
```

The measures of central tendencies of Offensive  salaries are as follows (in the order: Mean, Median, Mode)
```{r}
AvgOffenseSalary <- mean(OffenseSalary)
MedianOffenseSalary <- median(OffenseSalary)
ModeOffenseSalary <- Mode(OffenseSalary)
AvgOffenseSalary
MedianOffenseSalary
ModeOffenseSalary
```
The measures of variation for QB salaries are as follows (in the order: Range, Variation, Standard Deviation)
```{r}
RangeOffenseSalary <- range(OffenseSalary)
VarianceOffenseSalary <- var(OffenseSalary)
StdOffenseSalary <- sqrt(VarianceOffenseSalary)
RangeOffenseSalary
VarianceOffenseSalary
StdOffenseSalary
```
The Correlation test between Offensive Draft Position and Offensive Salary is as follows:
```{r}
cor.test(OffenseDraftOrders, OffenseSalary)
```
The linear regression between Offensive Draft Position and Offensive Salary is as follows:
```{r}
lm(OffenseSalary ~ OffenseDraftOrders)
```

Below is a scatterplot between the draft order and average salary of Quarterbacks and the Correlation
```{r}
plot(OffenseDraftOrders, OffenseSalary, main="Offensive Salary vs Offensive Draft Positions",
   xlab="Offensive Draft Positions", ylab="Offensive Salary (millions)", pch=19)
abline(lm(OffenseSalary ~ OffenseDraftOrders))
```

Below is a normality plot for Offensive Salary to determine if the sample is drawn from a normal distribution
```{r}
qqnorm(OffenseSalary)
qqline(OffenseSalary)
```

Outlier Check (The outliers of the Offense Salaries are listed below)
```{r}
OffenseOutliers <- FindOutliers(OffenseSalary)
OffenseOutliers
```

<<<<<<< Updated upstream
As you can see there are no outliers.

\pagebreak

The second positional side we are discussing will be the Defensive side (3 positions - DB, DL, and LB)
```{r}
DefensiveDraftOrders <- Defense$Draft.Order
DefenseSalary <- Defense$Avg.Salary
```

The measures of central tendencies of Defensive salaries are as follows (in the order: Mean, Median, Mode)
```{r}
AvgDefenseSalary <- mean(DefenseSalary)
MedianDefenseSalary <- median(DefenseSalary)
ModeDefenseSalary <- Mode(DefenseSalary)
AvgDefenseSalary
MedianDefenseSalary
ModeDefenseSalary
```
The measures of variation for QB salaries are as follows (in the order: Range, Variation, Standard Deviation)
```{r}
RangeDefenseSalary <- range(DefenseSalary)
VarianceDefenseSalary <- var(DefenseSalary)
StdDefenseSalary <- sqrt(VarianceDefenseSalary)
RangeDefenseSalary
VarianceDefenseSalary
StdDefenseSalary
```
The Correlation test between Offensive Draft Position and Offensive Salary is as follows:
```{r}
cor.test(DefensiveDraftOrders, DefenseSalary)
```
The linear regression between Offensive Draft Position and Offensive Salary is as follows:
```{r}
lm(DefenseSalary ~ DefensiveDraftOrders)
```

Below is a scatterplot between the draft order and average salary of Quarterbacks and the Correlation
```{r}
plot(DefensiveDraftOrders, DefenseSalary, main="Defensive Salary vs Defensive Draft Positions",
   xlab="Defensive Draft Positions", ylab="Defensive Salary (millions)", pch=19)
abline(lm(DefenseSalary ~ DefensiveDraftOrders))
```

Below is a normality plot for Offensive Salary to determine if the sample is drawn from a normal distribution
```{r}
qqnorm(DefenseSalary)
qqline(DefenseSalary)
```

Outlier Check (The outliers of the Offense Salaries are listed below)
```{r}
DefensiveOutliers <- FindOutliers(DefenseSalary)
DefensiveOutliers
```

As you can see there are no outliers.

For each position on defense, there are meaningful statistics for each defensive position. We will highlight and descirbe them below. 

DB: Interceptions (INTS)
LB: Combined Tackles and Sacks 
DL: Combined Tackles and Sacks

```{r}
MeanDBInts <- mean(DB_Data$Ints)
MeanDBInts
```
```{r}
MeanDLTackles <- mean(DL_Data$Tackles)
MeanDLSacks <- mean(DL_Data$Sacks)
MeanDLTackles
MeanDLSacks
```

```{r}
MeanLBTackles <- mean(LB_Data$Tackles)
MeanLBSacks <- mean(LB_Data$Sacks)
MeanLBTackles
MeanLBSacks
```






=======
As you can see there are no outliers

In the offense, we are combining 3 different positions; however, when we compare each position we must also consider skills independent to the position itself - not the entire offensive side of the ball. These statistics are not part of the correlation test, they are just for the readers reference as they will be used in arguments in the final project. For each 

QBs (Measures of Central Tendency and Variation for QBR)
```{r}
QB_Qbr <- QB_Data$QBR
mean(QB_Qbr)
median(QB_Qbr)
Mode(QB_Qbr)

range(QB_Qbr)
var(QB_Qbr)
sqrt(var(QB_Qbr))
```

RBs (Measures of Central Tendency and Variation for Average Touchdowns Scored)
```{r}
RB_TDs <- RB_Data$Touchdowns
mean(RB_TDs)
median(RB_TDs)
Mode(RB_TDs)

range(RB_TDs)
var(RB_TDs)
sqrt(var(RB_TDs))
```

WRs (Measures of Central Tendency and Variation for Average Touchdowns Scored)
```{r}
WR_TDs <- WR_Data$Touchdowns
mean(WR_TDs)
median(WR_TDs)
Mode(WR_TDs)

range(WR_TDs)
var(WR_TDs)
sqrt(var(WR_TDs))
```
>>>>>>> Stashed changes
